Whenever the data sample is fixed, the search for new signal is a well-established process. A fit to the multivariate discriminator distribution will be performed in order to estimate the amount of \fourtop events in selected samples. In this analysis a significant fraction of the background contamination is expected in the final datasets, therefore its shape and normalisation have to be determined preferably using data-driven approaches or employing theoretical predictions. A simultaneous fit to different background- (signal-) enhanced event categories can be performed to constrain the background and determine the number of signal events. I have a good knowledge of various fitting approaches, including multidimensional likelihood fits to the distributions with low counting statistics to effectively work on this task.

In both BSM searches and SM measurement (see below) the experimental and theoretical sources of systematic uncertainty have to be taken into account as both can affect the shape and normalisation of the measured distributions. Examples of theoretical uncertainty include the ones due to the variation of renormalisation and factorisation scales in perturbative calculations or the variation of the matching scale in the parton-shower-matching procedure. The experimental uncertainties arise, for example, due to finite jet and lepton energy resolutions, b- and top-identification procedures, luminosity etc. These uncertainties can be included as a nuisance parameters into the above-mentioned likelihood fits.

Individual channels will differ in the details of systematic studies, mainly because of the variations in the background strength and sources composition. The studies for single- and two-leptons channels will largely benefit from the experience developed by the host institute, while in the zero-leptons channel my expertise in QCD jet analysis will be a valuable complement.

\textbf{Overall, the described work package is assessed as high risk because it is contingent upon the progress in the previous WP. Moreover, the all-hadronic channel may require more significant effort investment, because of severe QCD background that is not completely understood}. Without doubt, the discovery of a new state will have major impact on the field, but negative result is also worth an effort since very little is known about this extreme corner of phase space. The obtained results will be \textbf{published in a refereed journal}.