\textbf{I am a co-author of more than 153 publications as a member of the CMS, ZEUS and CDF collaborations. These publications have on average 36 citations (per paper) and overall h-index  $h_\mathrm{HEP}=27$.} Moreover, for the contribution to the maintenance of the CMS Monte Carlo simulations production system I am be included in the CMS author list starting from 8 February 2016.

By convention, articles published by particle physics experiments list all collaboration members as authors in strict alphabetical order. This policy reflects the substantial efforts in detector construction and maintenance, data acquisition, data reconstruction and calibration that all collaborators contribute to and which is a prerequisite to any data analysis. This is particularly relevant for those who have committed a substantial fraction of their time to construction, installation and commissioning of detectors. As such, scientific leadership, which is awarded after selection on merits and excellence within the collaboration, as are conference presentations, and seminar invitations 
add a reliable additional measure of scientific productivity in the hep-ex field than merely citations alone.  The complete list of my publications is available from \url{http://inspirehep.net/search?ln=en&ln=en&p=find+a+lontkovskyi&of=hb&action_search=Search&sf=earliestdate&so=d&rm=&rg=25&sc=0}

\textbf{In 2016 I was invited as a referee for journal \textbf{Phys.Lett.B} (Impact factor 4.787).}
\begin{flushleft}
\textbf{List of the publications in peer-reviewed journals to which I made the main contribution:}\\
\end{flushleft}
\begin{enumerate}
	\item* ``Search for standard model production of four top quarks in proton-proton collisions at $\sqrt{s}$ = 13 TeV''\\
	By CMS Collaboration (A. M. Sirunyan {\it et al.}).	Phys.Lett.B 772 (2017) 336\\
	journal impact factor: 4.807\\
	also in CMS public document TOP-16-016\\
	cited 12 times as of 26 January 2018.\\
	I studied systematic effects attributed to the $b$-jet tagging, performed statistical combination of different searches and paper writing. As an exception, I was added to the CMS authors list for this publication, for my essential contribution.
	\item* ``Measurement of central exclusive $\pi^+ \pi^-$ production in $p\bar{p}$ collisions at $\sqrt{s} = 0.9$ and 1.96 TeV at CDF''\\
	By CDF Collaboration (Timo Antero Aaltonen et al.).	Physical Review \textbf{D 91} (2015) 9, 091101. \\
	journal impact factor:  4.506. \\
	cited 32 times as of 26 January 2018.\\
	I was one of the main analysers that developed and optimised the trigger chain for selection of exclusive central production events.
	\item* ``Inclusive-jet photoproduction at HERA and determination of alphas''\\
	By ZEUS Collaboration (H. Abramowicz et al.). 	Nuclear Physics \textbf{B 864} (2012) 1-37.\\
	10.1016/j.nuclphysb.2012.06.006.\\
	journal impact factor:  3.735. \\
	cited 42 times as of 26 January 2018. \\
	I was one of the main analysers that contributed to all stages of the analysis, including, MC studies, measurement unfolding, analysis of systematic uncetrainties, etc.
	\item*  ``The Pomeron and Odderon in elastic, inelastic and total cross sections at the LHC''\\
	By  L.L.~Jenkovszky, A.I.~Lengyel and D.I.~Lontkovskyi. International  Journal of Modern Physics {\bf A 26} (2011) 4755.\\
    journal impact factor:  1.699\\
	cited 31 times as of 26 January 2018. \\
	I was the main author of the model fits presented in the publication.
\end{enumerate}

\begin{flushleft}
\textbf{List of contributions to the conference proceedings}\\
\end{flushleft}
\begin{enumerate}
	\item ``Top quark physics at CMS'' by D.~Lontkovskyi (on behalf of CMS Collaboration).\\
	To be published in Proceedings of XXXI workshop Les Rencontres de Physique de la Vallée d'Aoste: La Tuile, Italy (2017).\\
	I presented a summary of CMS results on top physics.
	\item ``Proton structure measurements at HERA'' by D.~Lontkovskyi (for the H1 and ZEUS Collaboration).\\
	in Proceedings of 46th Rencontres de Moriond. QCD and High Energy Interactions: La Tuile, Italy (2012).\\
	I presented combined HERA summary results on behalf of the two collaborations.
	\item ``Jet cross sections in photoproduction at ZEUS'' by D.~Lontkovskyi (for the ZEUS Collaboration).\\
	in Proceedings of science, XVIII International Workshop on Deep-Inelastic Scattering and Related Subjects: Firenze, Italy (2010) 120.\\
	I presented preliminary results that were later published in [1].
\end{enumerate}
